---
title: "draft"
author: "iw"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We propose a set of measures to interpret level and timing of bereavement in a kinship network. 
This indicators reflects the implicit bereavement conditions in a certain population, not implying a specific shock or change.

Each measure is defined for a group or a single each kin type. Heterogeneity can be individual (by chance) or between groups. 

Let's start by creating a kinship network, in this case for Sweden 1950.

```{r cars}
library(DemoKin)
px <- swe_px[,"1950"]
fx <- swe_asfr[,'1950']
kin_net <- kin(px, fx)
head(kin_net$kin_full)
```

Now focus on daughters and mothers, to show what means each measure.

### Expected loss years, non-conditioned to Focal alive.

Prospective, years-kin to share, non-conditioned to Focal alive

$$\sum_{y=x}^{\omega-1}{\sum_{z=0}^{\omega-1}{d_k(y,z)\,e(z)}}$$

### Expected loss years, conditioned to Focal alive.

Prospective, years-kin to share, conditioned to Focal alive

$$\sum_{y=x}^{\omega-1}{\sum_{z=0}^{\omega-1}{d_k(y,z)\,e(y,z)}}$$

### Intensity of bereavement

Retrospective, portion died of accumulated perfect surviving kin, conditioned to Focal alive.

$$D_k(x)/L_k(x)$$

### Loneliness bereavement scale:

#### Age of potential absolute more lost (age with more living kin)

This age can be found in this terms: find the age $x$ where $k(x)$ is maximum. Can be found empirically for each case, but let's take a look to the analytics.

#### Age of potential relative more lost (age with less living kin)

This age can be found in this terms: find the age $x$ where $k(x)$ is minimum.

#### Age of more death experience

This age can be found in this terms: find the age $x$ where $d_k(x)$ is maximum. Is related to [Missov et.al (2015)](https://www.demographic-research.org/volumes/vol32/36/32-36.pdf) but weighted for each subsidy cohort.

### Time since lost

Being $\overline{a}_k(k)$ mean age at lost until age $a$:

$$\sum_{y=0}^{x-1}{\frac{d_k(y)}{D_k(x)}(x-y)}=x-\overline{a}_k(x)$$

### Prevalence of unexpected accumulated dead

What is an unexpected death?





```{r}
ex <- rev(cumsum(px))

```
